Busch, Khakhalin. Intrinsic temporal tuning

### 2019-06-10 reviews and responses.md

We replaced this sentence with the following one: "This was not necessarily surprising, as mechanosensory and visual inputs have different cellular targets in the tectum (Pratt and Aizenman, 2009; Felch et al., 2016; Truszkowski et al., 2017), potentially leading to different recruitment of tectal excitatory and inhibitory circuits. Acoustic stimuli may also be inherently weaker than visual stimuli in triggering plasticity effects in tectal neurons, as they arrive at different compartments within the dendritic tree (Hiramoto and Cline, 2009; Deeg et al., 2009), which may shape their influence on neuronal plasticity (Richards and Lillicrap, 2019)."

Here, the actual rationale for the second explanation (a difference in subcellular targets) is that inputs to different parts of the dentritic tree can trigger action potentials of different shape, and differentially affect calcium dynamics in the neuron, which, together with non-linear processing in dendrites may make different types of inputs unequal in terms of their effects on neuronal activity, and neuronal tuning, respectively. Two extreme examples of this effect would be the impact of climbing fibers on the activity of Purkinje cells in the cerebellum, or the impact of inputs to the apical dendrites of pyramidal cells in the cortex. We feel, however, that this topic is very complex, yet somewhat tangential to the main message of the paper, so we tried to limit our exposition into it by a short sentence and a good, recent reference.

> Page 13 line 46: The authors use the term “distributed sensory network” . Is a “distributed” network a
special type of sensory network?

Technically, even two neurons form a network (and a true mathematician would probably argue that even one neuron forms a network!), yet the tectal network is a relatively large one, with broad recurrent excitation, and in which different parts of the sensory input are processed in parallel. To subtly remind the reader about that, we used a word "distributed", as in "distributed computations", as opposed to more local and covergent networks, such as, for example, the Mauthner cell network in the hindbrain. This word is often used in writing (a Google Scholar search for `"distributed network" brain` returns 27000 hits), but admittedly it is not a precisely defined term, but rather a useful qualifier. We removed the word "distributed" from this sentence, in the interest of brevity, but retained it in the second paragraph of the Introduction.

@@

"To test this question, we exposed tadpoles to four hours of behaviorally salient, startle-inducing “click” sounds, provided at the same frequency (every second) as visual stimuli in the first set of experiments. We found (Fig 1D, E) that exposure to these sounds..."

> - Tadpoles are exposed to 4 hours of click sounds and then intrinsic tuning was measured. No difference
in spiking was observed. This was interpreted to mean that acoustic stimuli did “not strongly activate
tectal circuits during conditioning”. How can the authors know this? Instead, why not determine this
directly by recording click-evoked responses from tectal neurons? Or, if tectal cell responses to auditory
stimuli have been described in previous work, this should be included here.

Unfortunately, electrophysiological recording of tectal reponses to sounds in tadpoles does not seem to be technically feasible, not just in our lab (where we don't even have the technical capability to perform in-vivo experiments), but in most labs. From the technical point of view, the problem amounts to two limitations: one, to record from a tadpole, one has to paralyze it with a nicotinic receptor anatagonist, which seems to disrupt hearing. Second, even if this limitation could be overcome, the sounds have to be strong enough to stimulate the inner ear, but weak enough not to mechanically disrupt the recording. Conceivably, both challenges may be circumvented with the use of high speed calcum imaging in freely moving tadpoles, but to our knowledge no lab has attempted these recordings yet.

To show that our statement is just a conjecture, we replaced "suggests" with "may suggest" in this sentence: "This may suggest that acoustic stimuli did not activate tectal circuits strongly enough during conditioning..."

### 2019-06-10 merged.tex
Official resubmission

>>>>

\usepackage{filecontents}
\begin{filecontents}{localref.bib}

@article{lazar1973golgi,
  title={The development of the optic tectum in Xenopus laevis: a Golgi study.},
  author={Lazar, GY},
  journal={Journal of Anatomy},
  volume={116},
  number={Pt 3},
  pages={347},
  year={1973},
  publisher={Wiley-Blackwell}
}

@article{meredith1983,
  title={Interactions among converging sensory inputs in the superior colliculus},
  author={Meredith, M Alex and Stein, Barry E},
  journal={Science},
  volume={221},
  number={4608},
  pages={389--391},
  year={1983},
  publisher={American Association for the Advancement of Science}
}

@article{spruston1993,
  title={Voltage-and space-clamp errors associated with the measurement of electrotonically remote synaptic events},
  author={Spruston, Nelson and Jaffe, David B and Williams, Stephen H and Johnston, Daniel},
  journal={Journal of Neurophysiology},
  volume={70},
  number={2},
  pages={781--802},
  year={1993},
  publisher={Am Physiological Soc}
}

@article{destexhe1994,
  title={Synthesis of models for excitable membranes, synaptic transmission and neuromodulation using a common kinetic formalism},
  author={Destexhe, Alain and Mainen, Zachary F and Sejnowski, Terrence J},
  journal={Journal of computational neuroscience},
  volume={1},
  number={3},
  pages={195--230},
  year={1994},
  publisher={Springer}
}

@book{nieuwkoop1994,
  title={Normal table of Xenopus laevis (Daudin): A Systematical and Chronological Survey of the Development from the Fertilized Egg till the end of Metamorphosis.},
  author={Nieuwkoop, Pieter D and Faber, Jacob},
  year={1994}
}

@article{ma1996dynamic,
  title={The role of K+ currents in frequency-dependent spike broadening in Aplysia R20 neurons: a dynamic-clamp analysis},
  author={Ma, Minghong and Koester, John},
  journal={Journal of Neuroscience},
  volume={16},
  number={13},
  pages={4089--4101},
  year={1996},
  publisher={Soc Neuroscience}
}

@article{wu1996,
  title={Maturation of a central glutamatergic synapse},
  author={Wu, G-Y and Malinow, R and Cline, HT},
  journal={Science},
  volume={274},
  number={5289},
  pages={972--976},
  year={1996},
  publisher={American Association for the Advancement of Science}
}

@article{debanne1997,
  title={Action-potential propagation gated by an axonal I A-like K+ conductance in hippocampus},
  author={Debanne, Dominique and Guerineau, Nathalie C and G{\"a}hwiler, Beat H and Thompson, Scott M},
  journal={Nature},
  volume={389},
  number={6648},
  pages={286},
  year={1997},
  publisher={Nature Publishing Group}
}

@article{murakoshi1997kv2phosphorilation,
  title={Phosphorylation of the Kv2. 1 K+ channel alters voltage-dependent activation},
  author={Murakoshi, Hideyuki and Shi, Gongyi and Scannevin, Robert H and Trimmer, James S},
  journal={Molecular pharmacology},
  volume={52},
  number={5},
  pages={821--828},
  year={1997},
  publisher={ASPET}
}

@article{jaeger1999,
  title={Synaptic control of spiking in cerebellar Purkinje cells: dynamic current clamp based on model conductances},
  author={Jaeger, Dieter and Bower, James M},
  journal={Journal of Neuroscience},
  volume={19},
  number={14},
  pages={6090--6101},
  year={1999},
  publisher={Soc Neuroscience}
}

@article{kanold1999transient_k,
  title={Transient potassium currents regulate the discharge patterns of dorsal cochlear nucleus pyramidal cells},
  author={Kanold, Patrick O and Manis, Paul B},
  journal={Journal of Neuroscience},
  volume={19},
  number={6},
  pages={2195--2208},
  year={1999},
  publisher={Soc Neuroscience}
}

@article{stemmler1999information,
  title={How voltage-dependent conductances can adapt to maximize the information encoded by neuronal firing rate},
  author={Stemmler, Martin and Koch, Christof},
  journal={Nature neuroscience},
  volume={2},
  number={6},
  pages={521},
  year={1999},
  publisher={Nature Publishing Group}
}

@article{azouz2000threshold,
  title={Dynamic spike threshold reveals a mechanism for synaptic coincidence detection in cortical neurons in vivo},
  author={Azouz, Rony and Gray, Charles M},
  journal={Proceedings of the National Academy of Sciences},
  volume={97},
  number={14},
  pages={8110--8115},
  year={2000},
  publisher={National Acad Sciences}
}

@article{brenner2000,
  title={Adaptive rescaling maximizes information transmission},
  author={Brenner, Naama and Bialek, William and Van Steveninck, Rob de Ruyter},
  journal={Neuron},
  volume={26},
  number={3},
  pages={695--702},
  year={2000},
  publisher={Elsevier}
}

@article{hutcheon2000,
  title={Resonance, oscillation and the intrinsic frequency preferences of neurons},
  author={Hutcheon, Bruce and Yarom, Yosef},
  journal={Trends in neurosciences},
  volume={23},
  number={5},
  pages={216--222},
  year={2000},
  publisher={Elsevier}
}

@article{goldman2001,
  title={Global structure, robustness, and modulation of neuronal models},
  author={Goldman, Mark S and Golowasch, Jorge and Marder, Eve and Abbott, LF},
  journal={Journal of Neuroscience},
  volume={21},
  number={14},
  pages={5229--5238},
  year={2001},
  publisher={Soc Neuroscience}
}

@article{aizenman2002,
  title={Visually driven modulation of glutamatergic synaptic transmission is mediated by the regulation of intracellular polyamines},
  author={Aizenman, Carlos D and Munoz-Elias, Guillermo and Cline, Hollis T},
  journal={Neuron},
  volume={34},
  number={4},
  pages={623--634},
  year={2002},
  publisher={Elsevier}
}

@article{golowasch2002,
  title={Failure of averaging in the construction of a conductance-based neuron model},
  author={Golowasch, Jorge and Goldman, Mark S and Abbott, LF and Marder, Eve},
  journal={Journal of Neurophysiology},
  volume={87},
  number={2},
  pages={1129--1131},
  year={2002},
  publisher={Am Physiological Soc}
}

@article{aizenman2003,
  title={Visually driven regulation of intrinsic neuronal excitability improves stimulus detection in vivo},
  author={Aizenman, Carlos D and Akerman, Colin J and Jensen, Kendall R and Cline, Hollis T},
  journal={Neuron},
  volume={39},
  number={5},
  pages={831--842},
  year={2003},
  publisher={Elsevier}
}

@article{frank2003nachannels,
  title={Overview of the voltage-gated sodium channel family},
  author={Frank, H Yu and Catterall, William A},
  journal={Genome biology},
  volume={4},
  number={3},
  pages={207},
  year={2003},
  publisher={BioMed Central}
}

@article{prinz2004,
  title={The dynamic clamp comes of age},
  author={Prinz, Astrid A and Abbott, LF and Marder, Eve},
  journal={Trends in neurosciences},
  volume={27},
  number={4},
  pages={218--224},
  year={2004},
  publisher={Elsevier}
}

@article{prinz2004degeneracy,
  title={Similar network activity from disparate circuit parameters},
  author={Prinz, Astrid A and Bucher, Dirk and Marder, Eve},
  journal={Nature neuroscience},
  volume={7},
  number={12},
  pages={1345},
  year={2004},
  publisher={Nature Publishing Group}
}

@article{ishikane2005,
  title={Synchronized retinal oscillations encode essential information for escape behavior in frogs},
  author={Ishikane, Hiroshi and Gangi, Mie and Honda, Shoko and Tachibana, Masao},
  journal={Nature neuroscience},
  volume={8},
  number={8},
  pages={1087},
  year={2005},
  publisher={Nature Publishing Group}
}

@article{sporns2005,
  title={The human connectome: a structural description of the human brain},
  author={Sporns, Olaf and Tononi, Giulio and K{\"o}tter, Rolf},
  journal={PLoS computational biology},
  volume={1},
  number={4},
  pages={e42},
  year={2005},
  publisher={Public Library of Science}
}

@article{achard2006,
  title={Complex parameter landscape for a complex neuron model},
  author={Achard, Pablo and De Schutter, Erik},
  journal={PLoS computational biology},
  volume={2},
  number={7},
  pages={e94},
  year={2006},
  publisher={Public Library of Science}
}

@article{akerman2006,
  title={Depolarizing GABAergic conductances regulate the balance of excitation to inhibition in the developing retinotectal circuit in vivo},
  author={Akerman, Colin J and Cline, Hollis T},
  journal={Journal of Neuroscience},
  volume={26},
  number={19},
  pages={5117--5130},
  year={2006},
  publisher={Soc Neuroscience}
}

@article{kuba2006,
  title={Axonal site of spike initiation enhances auditory coincidence detection},
  author={Kuba, Hiroshi and Ishii, Takahiro M and Ohmori, Harunori},
  journal={Nature},
  volume={444},
  number={7122},
  pages={1069},
  year={2006},
  publisher={Nature Publishing Group}
}

@article{marder2006,
  title={Variability, compensation and homeostasis in neuron and network function},
  author={Marder, Eve and Goaillard, Jean-Marc},
  journal={Nature Reviews Neuroscience},
  volume={7},
  number={7},
  pages={563},
  year={2006},
  publisher={Nature Publishing Group}
}

@article{schulz2006,
  title={Variable channel expression in identified single and electrically coupled neurons in different animals},
  author={Schulz, David J and Goaillard, Jean-Marc and Marder, Eve},
  journal={Nature neuroscience},
  volume={9},
  number={3},
  pages={356},
  year={2006},
  publisher={Nature Publishing Group}
}

@article{aizenman2007,
  title={Enhanced visual activity in vivo forms nascent synapses in the developing retinotectal projection},
  author={Aizenman, Carlos D and Cline, Hollis T},
  journal={Journal of neurophysiology},
  volume={97},
  number={4},
  pages={2949--2957},
  year={2007},
  publisher={Am Physiological Soc}
}

@article{kole2007,
  title={Axon initial segment Kv1 channels control axonal action potential waveform and synaptic efficacy},
  author={Kole, Maarten HP and Letzkus, Johannes J and Stuart, Greg J},
  journal={Neuron},
  volume={55},
  number={4},
  pages={633--647},
  year={2007},
  publisher={Elsevier}
}

@article{pratt2007,
  title={Homeostatic regulation of intrinsic excitability and synaptic transmission in a developing visual circuit},
  author={Pratt, Kara G and Aizenman, Carlos D},
  journal={Journal of Neuroscience},
  volume={27},
  number={31},
  pages={8268--8277},
  year={2007},
  publisher={Soc Neuroscience}
}

@article{turrigiano2007,
  title={Homeostatic signaling: the positive side of negative feedback},
  author={Turrigiano, Gina},
  journal={Current opinion in neurobiology},
  volume={17},
  number={3},
  pages={318--324},
  year={2007},
  publisher={Elsevier}
}

@article{cline2008,
  title={The regulation of dendritic arbor development and plasticity by glutamatergic synaptic input: a review of the synaptotrophic hypothesis},
  author={Cline, Hollis and Haas, Kurt},
  journal={The Journal of physiology},
  volume={586},
  number={6},
  pages={1509--1517},
  year={2008},
  publisher={Wiley Online Library}
}

@article{ewald2008,
  title={Roles of NR2A and NR2B in the development of dendritic arbor morphology in vivo},
  author={Ewald, Rebecca C and Van Keuren-Jensen, Kendall R and Aizenman, Carlos D and Cline, Hollis T},
  journal={Journal of Neuroscience},
  volume={28},
  number={4},
  pages={850--861},
  year={2008},
  publisher={Soc Neuroscience}
}

@article{kole2008,
  title={Action potential generation requires a high sodium channel density in the axon initial segment},
  author={Kole, Maarten HP and Ilschner, Susanne U and Kampa, Bj{\"o}rn M and Williams, Stephen R and Ruben, Peter C and Stuart, Greg J},
  journal={Nature neuroscience},
  volume={11},
  number={2},
  pages={178},
  year={2008},
  publisher={Nature Publishing Group}
}

@article{narayanan2008,
  title={The h channel mediates location dependence and plasticity of intrinsic phase response in rat hippocampal neurons},
  author={Narayanan, Rishikesh and Johnston, Daniel},
  journal={Journal of Neuroscience},
  volume={28},
  number={22},
  pages={5846--5860},
  year={2008},
  publisher={Soc Neuroscience}
}

@article{pratt2008,
  title={Development and spike timing--dependent plasticity of recurrent excitation in the Xenopus optic tectum},
  author={Pratt, Kara G and Dong, Wei and Aizenman, Carlos D},
  journal={Nature neuroscience},
  volume={11},
  number={4},
  pages={467},
  year={2008},
  publisher={Nature Publishing Group}
}

@article{bollmann2009,
  title={Subcellular topography of visually driven dendritic activity in the vertebrate visual system},
  author={Bollmann, Johann H and Engert, Florian},
  journal={Neuron},
  volume={61},
  number={6},
  pages={895--905},
  year={2009},
  publisher={Elsevier}
}

@article{deeg2009,
  title={Development of multisensory convergence in the Xenopus optic tectum},
  author={Deeg, Katherine E and Sears, Irina B and Aizenman, Carlos D},
  journal={Journal of Neurophysiology},
  volume={102},
  number={6},
  pages={3392--3404},
  year={2009},
  publisher={American Physiological Society Bethesda, MD}
}

@article{dong2009,
  title={Visual avoidance in Xenopus tadpoles is correlated with the maturation of visual responses in the optic tectum},
  author={Dong, Wei and Lee, Ryan H and Xu, Heng and Yang, Shelley and Pratt, Kara G and Cao, Vania and Song, Yoon-Kyu and Nurmikko, Arto and Aizenman, Carlos D},
  journal={Journal of neurophysiology},
  volume={101},
  number={2},
  pages={803--815},
  year={2009},
  publisher={Am Physiological Soc}
}

@article{giocomo2009,
  title={Knock-out of HCN1 subunit flattens dorsal--ventral frequency gradient of medial entorhinal neurons in adult mice},
  author={Giocomo, Lisa M and Hasselmo, Michael E},
  journal={Journal of Neuroscience},
  volume={29},
  number={23},
  pages={7625--7630},
  year={2009},
  publisher={Soc Neuroscience}
}

@article{goaillard2009,
  title={Functional consequences of animal-to-animal variation in circuit parameters},
  author={Goaillard, Jean-Marc and Taylor, Adam L and Schulz, David J and Marder, Eve},
  journal={Nature neuroscience},
  volume={12},
  number={11},
  pages={1424},
  year={2009},
  publisher={Nature Publishing Group}
}

@article{hiramoto2009,
  title={Convergence of multisensory inputs in Xenopus tadpole tectum},
  author={Hiramoto, Masaki and Cline, Hollis T},
  journal={Developmental neurobiology},
  volume={69},
  number={14},
  pages={959--971},
  year={2009},
  publisher={Wiley Online Library}
}

@article{lukovsevivcius2009,
  title={Reservoir computing approaches to recurrent neural network training},
  author={Luko{\v{s}}evi{\v{c}}ius, Mantas and Jaeger, Herbert},
  journal={Computer Science Review},
  volume={3},
  number={3},
  pages={127--149},
  year={2009},
  publisher={Elsevier}
}

@article{marcelin2009,
  title={H channel-dependent deficit of theta oscillation resonance and phase shift in temporal lobe epilepsy},
  author={Marcelin, B{\'e}atrice and Chauvi{\`e}re, La{\"e}titia and Becker, Albert and Migliore, Michele and Esclapez, Monique and Bernard, Christophe},
  journal={Neurobiology of disease},
  volume={33},
  number={3},
  pages={436--447},
  year={2009},
  publisher={Elsevier}
}

@article{pratt2009trigeminal,
  title={Multisensory integration in mesencephalic trigeminal neurons in Xenopus tadpoles},
  author={Pratt, Kara G and Aizenman, Carlos D},
  journal={Journal of neurophysiology},
  volume={102},
  number={1},
  pages={399--412},
  year={2009},
  publisher={Am Physiological Soc}
}

@article{taylor2009,
  title={How multiple conductances determine electrophysiological properties in a multicompartment model},
  author={Taylor, Adam L and Goaillard, Jean-Marc and Marder, Eve},
  journal={Journal of Neuroscience},
  volume={29},
  number={17},
  pages={5573--5586},
  year={2009},
  publisher={Soc Neuroscience}
}

@article{branco2010dendritic,
  title={Dendritic discrimination of temporal input sequences in cortical neurons},
  author={Branco, Tiago and Clark, Beverley A and H{\"a}usser, Michael},
  journal={Science},
  volume={329},
  number={5999},
  pages={1671--1675},
  year={2010},
  publisher={American Association for the Advancement of Science}
}

@article{clopath2010stdp,
  title={Connectivity reflects coding: a model of voltage-based STDP with homeostasis},
  author={Clopath, Claudia and B{\"u}sing, Lars and Vasilaki, Eleni and Gerstner, Wulfram},
  journal={Nature neuroscience},
  volume={13},
  number={3},
  pages={344},
  year={2010},
  publisher={Nature Publishing Group}
}

@article{grashow2010,
  title={Compensation for variable intrinsic neuronal excitability by circuit-synaptic interactions},
  author={Grashow, Rachel and Brookings, Ted and Marder, Eve},
  journal={Journal of Neuroscience},
  volume={30},
  number={27},
  pages={9145--9156},
  year={2010},
  publisher={Soc Neuroscience}
}

@article{grubb2010activity,
  title={Activity-dependent relocation of the axon initial segment fine-tunes neuronal excitability},
  author={Grubb, Matthew S and Burrone, Juan},
  journal={Nature},
  volume={465},
  number={7301},
  pages={1070},
  year={2010},
  publisher={Nature Publishing Group}
}

@article{fiete2010stdp,
  title={Spike-time-dependent plasticity and heterosynaptic competition organize networks to produce long scale-free sequences of neural activity},
  author={Fiete, Ila R and Senn, Walter and Wang, Claude ZH and Hahnloser, Richard HR},
  journal={Neuron},
  volume={65},
  number={4},
  pages={563--576},
  year={2010},
  publisher={Elsevier}
}

@article{kuba2010initial,
  title={Presynaptic activity regulates Na+ channel distribution at the axon initial segment},
  author={Kuba, Hiroshi and Oichi, Yuki and Ohmori, Harunori},
  journal={Nature},
  volume={465},
  number={7301},
  pages={1075},
  year={2010},
  publisher={Nature Publishing Group}
}

@article{markram2010,
  title={The intense world theory--a unifying theory of the neurobiology of autism},
  author={Markram, Kamila and Markram, Henry},
  journal={Frontiers in human neuroscience},
  volume={4},
  pages={224},
  year={2010},
  publisher={Frontiers}
}

@misc{calabrese2011,
  title={Coping with variability in small neuronal networks},
  author={Calabrese, Ronald L and Norris, Brian J and Wenning, Angela and Wright, Terrence M},
  year={2011},
  publisher={Oxford University Press}
}

@article{deeg2011,
  title={Sensory modality--specific homeostatic plasticity in the developing optic tectum},
  author={Deeg, Katherine E and Aizenman, Carlos D},
  journal={Nature neuroscience},
  volume={14},
  number={5},
  pages={548},
  year={2011},
  publisher={Nature Publishing Group}
}

@article{marder2011,
  title={Multiple models to capture the variability in biological neurons and networks},
  author={Marder, Eve and Taylor, Adam L},
  journal={Nature neuroscience},
  volume={14},
  number={2},
  pages={133},
  year={2011},
  publisher={Nature Publishing Group}
}

@article{platkiewicz2011,
  title={Impact of fast sodium channel inactivation on spike threshold dynamics and synaptic integration},
  author={Platkiewicz, Jonathan and Brette, Romain},
  journal={PLoS computational biology},
  volume={7},
  number={5},
  pages={e1001129},
  year={2011},
  publisher={Public Library of Science}
}

@article{popovic2011,
  title={The spatio-temporal characteristics of action potential initiation in layer 5 pyramidal neurons: a voltage imaging study},
  author={Popovic, Marko A and Foust, Amanda J and McCormick, David A and Zecevic, Dejan},
  journal={The Journal of physiology},
  volume={589},
  number={17},
  pages={4167--4187},
  year={2011},
  publisher={Wiley Online Library}
}

@article{rubinov2011,
  title={Neurobiologically realistic determinants of self-organized criticality in networks of spiking neurons},
  author={Rubinov, Mikail and Sporns, Olaf and Thivierge, Jean-Philippe and Breakspear, Michael},
  journal={PLoS computational biology},
  volume={7},
  number={6},
  pages={e1002038},
  year={2011},
  publisher={Public Library of Science}
}

@article{shen2011,
  title={Inhibition to excitation ratio regulates visual system responses and behavior in vivo},
  author={Shen, Wanhua and McKeown, Caroline R and Demas, James A and Cline, Hollis T},
  journal={Journal of neurophysiology},
  volume={106},
  number={5},
  pages={2285--2302},
  year={2011},
  publisher={American Physiological Society Bethesda, MD}
}

@article{sridharan2011,
  title={Space coding by gamma oscillations in the barn owl optic tectum},
  author={Sridharan, Devarajan and Boahen, Kwabena and Knudsen, Eric I},
  journal={Journal of neurophysiology},
  volume={105},
  number={5},
  pages={2005--2017},
  year={2011},
  publisher={American Physiological Society Bethesda, MD}
}

@article{turrigiano2011,
  title={Too many cooks? Intrinsic and synaptic homeostatic mechanisms in cortical circuit refinement},
  author={Turrigiano, Gina},
  journal={Annual review of neuroscience},
  volume={34},
  pages={89--103},
  year={2011},
  publisher={Annual Reviews}
}

@article{xu2011,
  title={Visual experience-dependent maturation of correlated neuronal activity patterns in a developing visual system},
  author={Xu, Heng and Khakhalin, Arseny S and Nurmikko, Arto V and Aizenman, Carlos D},
  journal={Journal of Neuroscience},
  volume={31},
  number={22},
  pages={8025--8036},
  year={2011},
  publisher={Soc Neuroscience}
}

@article{baranauskas2012,
  title={20 Hz membrane potential oscillations are driven by synaptic inputs in collision-detecting neurons in the frog optic tectum},
  author={Baranauskas, Gytis and Svirskiene, Natasa and Svirskis, Gytis},
  journal={Neuroscience letters},
  volume={528},
  number={2},
  pages={196--200},
  year={2012},
  publisher={Elsevier}
}

@article{bianchi2012,
  title={On the mechanisms underlying the depolarization block in the spiking dynamics of CA1 pyramidal neurons},
  author={Bianchi, Daniela and Marasco, Addolorata and Limongiello, Alessandro and Marchetti, Cristina and Marie, Helene and Tirozzi, Brunello and Migliore, Michele},
  journal={Journal of computational neuroscience},
  volume={33},
  number={2},
  pages={207--225},
  year={2012},
  publisher={Springer}
}

@article{clay2012optimal,
  title={Ionic mechanism underlying optimal stimuli for neuronal excitation: role of Na+ channel inactivation},
  author={Clay, John R and Forger, Daniel B and Paydarfar, David},
  journal={PloS one},
  volume={7},
  number={9},
  pages={e45983},
  year={2012},
  publisher={Public Library of Science}
}

@article{goddard2012,
  title={Gamma oscillations are generated locally in an attention-related midbrain network},
  author={Goddard, C Alex and Sridharan, Devarajan and Huguenard, John R and Knudsen, Eric I},
  journal={Neuron},
  volume={73},
  number={3},
  pages={567--580},
  year={2012},
  publisher={Elsevier}
}

@article{khakhalin2012,
  title={GABAergic transmission and chloride equilibrium potential are not modulated by pyruvate in the developing optic tectum of Xenopus laevis tadpoles},
  author={Khakhalin, Arseny S and Aizenman, Carlos D},
  journal={PLoS One},
  volume={7},
  number={4},
  pages={e34446},
  year={2012},
  publisher={Public Library of Science}
}

@article{kole2012,
  title={Signal processing in the axon initial segment},
  author={Kole, Maarten HP and Stuart, Greg J},
  journal={Neuron},
  volume={73},
  number={2},
  pages={235--247},
  year={2012},
  publisher={Elsevier}
}

@article{kuba2012,
  title={Structural tuning and plasticity of the axon initial segment in auditory neurons},
  author={Kuba, Hiroshi},
  journal={The Journal of physiology},
  volume={590},
  number={22},
  pages={5571--5579},
  year={2012},
  publisher={Wiley Online Library}
}

@article{bengio2013,
  title={Representation learning: A review and new perspectives},
  author={Bengio, Yoshua and Courville, Aaron and Vincent, Pascal},
  journal={IEEE transactions on pattern analysis and machine intelligence},
  volume={35},
  number={8},
  pages={1798--1828},
  year={2013},
  publisher={IEEE}
}

@article{colgin2013,
  title={Mechanisms and functions of theta rhythms},
  author={Colgin, Laura Lee},
  journal={Annual review of neuroscience},
  volume={36},
  pages={295--312},
  year={2013},
  publisher={Annual Reviews}
}

@article{kirkby2013,
  title={A role for correlated spontaneous activity in the assembly of neural circuits},
  author={Kirkby, Lowry A and Sack, Georgeann S and Firl, Alana and Feller, Marla B},
  journal={Neuron},
  volume={80},
  number={5},
  pages={1129--1144},
  year={2013},
  publisher={Elsevier}
}

@article{oleary2013,
  title={Correlations in ion channel expression emerge from homeostatic tuning rules},
  author={O'Leary, Timothy and Williams, Alex H and Caplan, Jonathan S and Marder, Eve},
  journal={Proceedings of the National Academy of Sciences},
  volume={110},
  number={28},
  pages={E2645--E2654},
  year={2013},
  publisher={National Acad Sciences}
}

@article{pratt2013,
  title={Modeling human neurodevelopmental disorders in the Xenopus tadpole: from mechanisms to therapeutic targets},
  author={Pratt, Kara G and Khakhalin, Arseny S},
  journal={Disease models \& mechanisms},
  pages={dmm--012138},
  year={2013},
  publisher={The Company of Biologists Ltd}
}

@book{venables2013,
  title={Modern applied statistics with S-PLUS},
  author={Venables, William N and Ripley, Brian D},
  year={2013},
  publisher={Springer Science \& Business Media}
}

@article{bates2014,
  title={Fitting linear mixed-effects models using lme4},
  author={Bates, Douglas and M{\"a}chler, Martin and Bolker, Ben and Walker, Steve},
  journal={arXiv preprint arXiv:1406.5823},
  year={2014}
}

@article{beatty2014,
  title={Cell-type-specific resonances shape the responses of striatal neurons to synaptic input},
  author={Beatty, Joseph A and Song, Soomin C and Wilson, Charles J},
  journal={Journal of neurophysiology},
  volume={113},
  number={3},
  pages={688--700},
  year={2014},
  publisher={American Physiological Society Bethesda, MD}
}

@article{fontaine2014threshold,
  title={Spike-threshold adaptation predicted by membrane potential dynamics in vivo},
  author={Fontaine, Bertrand and Pe{\~n}a, Jos{\'e} Luis and Brette, Romain},
  journal={PLoS computational biology},
  volume={10},
  number={4},
  pages={e1003560},
  year={2014},
  publisher={Public Library of Science}
}

@article{hamodi2014,
  title={Region-specific regulation of voltage-gated intrinsic currents in the developing optic tectum of the Xenopus tadpole},
  author={Hamodi, Ali S and Pratt, Kara G},
  journal={Journal of neurophysiology},
  volume={112},
  number={7},
  pages={1644--1655},
  year={2014},
  publisher={Am Physiological Soc}
}

@article{khakhalin2014,
  title={Excitation and inhibition in recurrent networks mediate collision avoidance in Xenopus tadpoles},
  author={Khakhalin, Arseny S and Koren, David and Gu, Jenny and Xu, Heng and Aizenman, Carlos D},
  journal={European Journal of Neuroscience},
  volume={40},
  number={6},
  pages={2948--2962},
  year={2014},
  publisher={Wiley Online Library}
}

@article{stein2014,
  title={Development of multisensory integration from the perspective of the individual neuron},
  author={Stein, Barry E and Stanford, Terrence R and Rowland, Benjamin A},
  journal={Nature Reviews Neuroscience},
  volume={15},
  number={8},
  pages={520},
  year={2014},
  publisher={Nature Publishing Group}
}

@article{takemura2014,
  title={Connectome of the fly visual circuitry},
  author={Takemura, Shin-ya},
  journal={Microscopy},
  volume={64},
  number={1},
  pages={37--44},
  year={2014},
  publisher={Oxford University Press}
}

@article{ciarleglio2015,
  title={Multivariate analysis of electrophysiological diversity of Xenopus visual neurons during development and plasticity},
  author={Ciarleglio, Christopher M and Khakhalin, Arseny S and Wang, Angelia F and Constantino, Alexander C and Yip, Sarah P and Aizenman, Carlos D},
  journal={Elife},
  volume={4},
  year={2015},
  publisher={eLife Sciences Publications, Ltd}
}

@article{drion2015,
  title={Ion channel degeneracy enables robust and tunable neuronal firing rates},
  author={Drion, Guillaume and O’Leary, Timothy and Marder, Eve},
  journal={Proceedings of the National Academy of Sciences},
  volume={112},
  number={38},
  pages={E5361--E5370},
  year={2015},
  publisher={National Acad Sciences}
}

@article{evans2015,
  title={Rapid modulation of axon initial segment length influences repetitive spike firing},
  author={Evans, Mark D and Dumitrescu, Adna S and Kruijssen, Dennis LH and Taylor, Samuel E and Grubb, Matthew S},
  journal={Cell reports},
  volume={13},
  number={6},
  pages={1233--1245},
  year={2015},
  publisher={Elsevier}
}

@article{james2015,
  title={Valproate-induced neurodevelopmental deficits in Xenopus laevis tadpoles},
  author={James, Eric J and Gu, Jenny and Ramirez-Vizcarrondo, Carolina M and Hasan, Mashfiq and Truszkowski, Torrey LS and Tan, Yuqi and Oupravanh, Phouangmaly M and Khakhalin, Arseny S and Aizenman, Carlos D},
  journal={Journal of Neuroscience},
  volume={35},
  number={7},
  pages={3218--3229},
  year={2015},
  publisher={Soc Neuroscience}
}

@article{lecun2015,
  title={Deep learning},
  author={LeCun, Yann and Bengio, Yoshua and Hinton, Geoffrey},
  journal={Nature},
  volume={521},
  number={7553},
  pages={436},
  year={2015},
  publisher={Nature Publishing Group}
}

@book{mccarthy2015,
  title={Getting Started with P5. js: Making Interactive Graphics in JavaScript and Processing},
  author={McCarthy, Lauren and Reas, Casey and Fry, Ben},
  year={2015},
  publisher={Maker Media, Inc.}
}

@article{radford2015,
  title={Unsupervised representation learning with deep convolutional generative adversarial networks},
  author={Radford, Alec and Metz, Luke and Chintala, Soumith},
  journal={arXiv preprint arXiv:1511.06434},
  year={2015}
}

@article{cropper2016,
  title={Consequences of degeneracy in network function},
  author={Cropper, Elizabeth C and Dacks, Andrew M and Weiss, Klaudiusz R},
  journal={Current opinion in neurobiology},
  volume={41},
  pages={62--67},
  year={2016},
  publisher={Elsevier}
}

@article{felch2016,
  title={Multisensory integration in the developing tectum is constrained by the balance of excitation and inhibition},
  author={Felch, Daniel L and Khakhalin, Arseny S and Aizenman, Carlos D},
  journal={Elife},
  volume={5},
  year={2016},
  publisher={eLife Sciences Publications, Ltd}
}

@article{grossberg2016,
  title={Resonant cholinergic dynamics in cognitive and motor decision-making: attention, category learning, and choice in neocortex, superior colliculus, and optic tectum},
  author={Grossberg, Stephen and Palma, Jesse and Versace, Massimiliano},
  journal={Frontiers in neuroscience},
  volume={9},
  pages={501},
  year={2016},
  publisher={Frontiers}
}

@article{hamada2016,
  title={Covariation of axon initial segment location and dendritic tree normalizes the somatic action potential},
  author={Hamada, Mustafa S and Goethals, Sarah and de Vries, Sharon I and Brette, Romain and Kole, Maarten HP},
  journal={Proceedings of the National Academy of Sciences},
  volume={113},
  number={51},
  pages={14841--14846},
  year={2016},
  publisher={National Acad Sciences}
}

@article{hamodi2016,
  title={An NMDA receptor-dependent mechanism for subcellular segregation of sensory inputs in the tadpole optic tectum},
  author={Hamodi, Ali S and Liu, Zhenyu and Pratt, Kara G},
  journal={eLife},
  volume={5},
  year={2016},
  publisher={eLife Sciences Publications, Ltd}
}
